Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
This study \cite{rca-alibaba} uses distributed tracing to perform
Diagnostics of performance degradation on a system by performing graph analysis on
trace level in real-time to determine the root cause of performance degradation or
root cause. This approach was developed based on performance profiling, tracking,
and logging system in Alibaba data center to speed up root cause diagnosis
in real-time. The developed system allows the discovery of normative patterns
and corresponding key graph properties, which are saved and updated offline
as a knowledge base for further use in risk estimation at the level of
trace and identify transitions that are unexpected deviations from the state
normal as shown in Fig. \ref{rc}.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch2/rca-framework.png}
	\caption{Workflow of Root-cause Analysis on \cite{rca-alibaba}}
	\label{rca-framwork}
\end{figure}

>>>>

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
This study \cite{rca-alibaba} uses distributed tracing to perform
Diagnostics of performance degradation on a system by performing graph analysis on
trace level in real-time to determine the root cause of performance degradation or
root cause. This approach was developed based on performance profiling, tracking, and logging system in Alibaba datacenter to speed up root cause diagnosis in real-time. The developed system allows the discovery of normative patterns and corresponding key graph properties, which are saved and updated offline as a knowledge base for further use in risk estimation at the trace level and identify transitions that are unexpected deviations from the normal
normal as shown in Fig. \ref{rc}.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch2/rca-framework.png}
	\caption{Workflow of Root-cause Analysis on \cite{rca-alibaba}}
	\label{rca-framwork}
\end{figure}
